Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-02-08 PAPER.tex
typo

Because $\widehat{\textbf{C}}$ is estimated from the data, its eigenvectors and eigenvalues are strongly coupled to the particular data realization that was used to compute it. For example, the strongest mode of $\widehat{\textbf{C}}$ (highest eigenvalue) describes the sinusoid foreground mode in the toy model (the first peak in Figure \ref{fig:toy_sigloss2}). In Figure \ref{fig:toy_sigloss12} we show the covariances of our toy model datasets along with inverse covariance weighted data. The foreground sinusoid is clearly visible in $\widehat{\textbf{C}}_{FG}$.

>>>>

Because $\widehat{\textbf{C}}$ is estimated from the data, its eigenvectors and eigenvalues are strongly coupled to the particular data realization that was used to compute it. For example, the strongest mode of $\widehat{\textbf{C}}$ (highest eigenvalue) describes the sinusoid foreground mode in the toy model (the peak in Figure \ref{fig:toy_sigloss3}). In Figure \ref{fig:toy_sigloss12} we show the covariances of our toy model datasets along with inverse covariance weighted data. The foreground sinusoid is clearly visible in $\widehat{\textbf{C}}_{FG}$.
